---
title: "Risk premium using GLMs, QR, QRII, PQR and ER"
output:
  html_document:
    highlight: tango
    theme: readable
    toc: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
---


## Load packages

```{r echo=TRUE, message=FALSE, warning=FALSE}
  library(data.table)
  library(gamlss)
  library(quantreg)
  library(qrcm)
  library(knitr)     # kable
  library(cplm)      # cpqlm
  library(tweedie)
  library(expectreg)

# define the logistic link function with exposures
  logitexp <- function(exposure = 1){
    linkfun <- function(mu) {            
      eta <- if (any(exposure-mu <= 0)) log((mu)/abs(mu-exposure)) else log((mu)/(exposure-mu))
      eta 
    }
    
    linkinv <- function(eta) {
      thresh <- -log(.Machine$double.eps)
      eta <- pmin(thresh, pmax(eta, -thresh))
      exposure*(exp(eta)/(1 + exp(eta)))
    }
    
    mu.eta <- function(eta) {
      thresh <- -log(.Machine$double.eps)
      res <- rep(.Machine$double.eps, length(eta))
      res[abs(eta) < thresh] <- ((exposure*exp(eta))/(1 + exp(eta))^2)[abs(eta) < thresh]
      res
    }
    
    valideta <- function(eta) TRUE 
    link <- paste("logexp(", exposure, ")", sep="") 
    structure(list(linkfun = linkfun, linkinv = linkinv, mu.eta = mu.eta, 
                   valideta = valideta, name = link), class = "link-glm") 
  }

```



## Section 4: Simulation study

### Case: MSE and sample variance of the estimated risk premium with respect to the values of the risk loading parameter $\varphi$

```{r message=FALSE, warning=FALSE, eval=FALSE}
set.seed(111)
Nsim <- 2000
mse.mat <- matrix(0, nrow = Nsim, ncol = 4) # mse results
colnames(rmse.mat) <- c('QR', 'QRCF', "QRII" ,'EQR') # the competing models
alpha.vector <- seq(from = 0, to = 0.15, by = 0.02) # risk loading parameters
alpha.vector <- alpha.vector[-1]
pars <- c(120, 1.65) # power and dispersion parameter in tweedie distribution

mse <- svar.mse  <- matrix(NA, nrow = length(alpha.vector), 4)

for (j in 1:length(alpha.vector)){
  alpha <- alpha.vector[j]
  for(k in 1:Nsim){
    nsample <- 5000
    x1sim <- rbinom(n = nsample, size = 1, prob = 0.6) # covariates
    x2sim <- rbinom(n = nsample, size = 1, prob = 0.8)
    x3sim <- rbinom(n = nsample, size = 1, prob = 0.5)
    beta <- c(4, 0.5, 0.5, 0.5) # coffieients
    X <- model.matrix( ~ x1sim + x2sim + x3sim) # Regression coefficients
    mu <- as.vector(exp(X%*%beta)) # mean parameter in tweedie distribution
    
    
    phi <- pars[1] # dispersion parameter
    p <- pars[2]   # power parameter
    # true value of C, Pure premium, and Risk prmeium
    C <- sum((1 + alpha)*mu) # risk loading parameter is 10% using expected value premium principle
    E.L <- sum(mu) # true pure premium
    riskP <- mu*(1 + alpha) # true risk premium for dt
    ysim <- 0
    for(i in 1:nsample){
      ysim[i] <- rtweedie(n = 1, mu = mu[i], phi = phi, power = p)
    }
    
    dt <- data.table(x1 = x1sim,
                     x2 = x2sim,
                     x3 = x3sim,
                     y = ysim,
                     clm = ifelse(ysim == 0, 0, 1))
    dt0 <- dt[y > 0]
    dt$count <- 1
    dt.sum     <- dt[, .( y = sum(y), Npolicies = sum(count)),
                     by = c('x1', 'x2', 'x3')
    ]
    dt.sum <- dt.sum[order(x1, x2, x3)] # tariff classes for prediction
    # logistic regression
    m_clm     <- glm(clm ~ x1 + x2 + x3, family = binomial(link = "logit"), data = dt)
    X1        <- model.matrix( ~ x1 + x2 + x3, data = dt.sum)
    beta_pred <- coef(m_clm)
    eta_pred  <- X1%*%beta_pred
    pi.pred   <- 1 - (exp(eta_pred)/(1+exp(eta_pred)))
    dt.sum$pi.pred <- pi.pred
    dt.sum$mu <- exp(X1%*%beta)
    # true risk premium 
    dt.sum$riskP <- (1 + alpha)*dt.sum$mu

    ## =======================================================================
    # Two-part GLMs: Logistic + gamma
    ## =======================================================================
    # 0-1 claim or not part
    m_clm     <- glm(clm ~ x1 + x2 + x3, family = binomial(link = "logit"), data = dt)
    X_pred    <- model.matrix( ~ x1 + x2 + x3, data = dt)
    beta_pred <- coef(m_clm)
    eta_pred  <- X_pred%*%beta_pred
    pi_pred   <- 1 - (exp(eta_pred)/(1+exp(eta_pred)))#*dt$exposure
    
    # claim > 0 claim amount part
    m.claim   <- glm(y ~ x1 + x2 + x3, family = Gamma(link='log'), data = dt0)
    X_pred    <- model.matrix( ~ x1 + x2 + x3, data = dt)
    beta_pred <- coef(m.claim)
    y_pred    <- exp(X_pred%*%beta_pred)
    
    
    
    #-----------------------------
    # prediction for dt.sum
    #-----------------------------
    X1        <- model.matrix( ~ x1 + x2 + x3, data = dt.sum)
    beta_pred <- coef(m_clm)
    eta_pred  <- X1%*%beta_pred
    pi.pred   <- 1 - (exp(eta_pred)/(1 + exp(eta_pred)))  # non-claim probability (exposure=1)
    beta_pred <- coef(m.claim)
    mu        <- exp(X1%*%beta_pred)
    E.ga      <- (1 - pi.pred)*mu
    
    dt.sum$Pure    <- E.ga                     # pure premium
    
    
    ## =======================================================================
    # Two-part quantile regressions
    # QR & PQR(QRCF) & ER
    ## =======================================================================
    
    theta <- 0.95 # quantile level
    dt.sum$theta_star <- (theta - dt.sum$pi.pred)/(1 - dt.sum$pi.pred) # non-zero quantile level
    #-----------------------------
    # QR model
    #-----------------------------
    dt$QR.95 <- 0
    for(i in 1:nrow(dt.sum)){
      m.s     <- rq(log(y) ~ x1 + x2 + x3, data = dt0, tau = dt.sum$theta_star[i])  # QR model
      TraQuan <- exp(predict(m.s, newdata = dt.sum))#*(1-dt.sum$pi.pred) # prediction
      dt.sum$QR.95[i] <- TraQuan[i]
    }
    qr.alpha <<- (C - E.L)/(sum(dt.sum$QR.95*dt.sum$Npolicies) - E.L) 
    
    #-----------------------------
    # QR
    # Risk class prediction (dt.sum) 
    #-----------------------------
    dt.sum$QR <- dt.sum$Pure + qr.alpha*(dt.sum$QR.95 - dt.sum$Pure) 
    dt.sum$loading.QR <- dt.sum$QR - dt.sum$Pure                        
    
    
    #-----------------------------
    # QRII model
    # Risk class prediction (dt.sum) 
    #-----------------------------
    theta_solve <- function(theta){
      m.s  <- rq(log(y) ~ x1 + x2 + x3, data = dt0, tau = theta) 
      flag <- exp(predict(m.s, newdata = dt.sum))*(1-dt.sum$pi.pred)
      bias <- C - sum(flag*dt.sum$Npolicies)
      return(bias)
    }
    upper_theta <- 0.99999
    lower_theta <- 0.00000001
    library(rootSolve)
    # solve the quantile level (risk loading parameter in QRII)
    m_solve <- uniroot(f       = theta_solve,
                       lower   = lower_theta,
                       upper   = upper_theta,
                       maxiter = 50000,
                       tol     = .Machine$double.eps^0.525) 
    theta_Tra <- m_solve$root
    m.s  <- rq(log(y) ~ x1 + x2 + x3, data = dt0, tau = theta_Tra) 
    flag <- exp(predict(m.s, newdata = dt.sum))*(1-dt.sum$pi.pred)
    dt.sum$QRII <- flag
    
    #-----------------------------
    # PQR(QRCF) model
    # solve risk loading parameter 
    #-----------------------------
    m3.s <- iqr(log(y) ~ x1 + x2 + x3,
                data      = dt0,
                formula.p = ~ slp(p,3))
    dt.sum$QRCF.95 <- 0
    for(i in 1:nrow(dt.sum)){
      flag <- predict(m3.s, type = "QF", p = dt.sum$theta_star[i], newdata = dt.sum)
      dt.sum$QRCF.95[i] <- exp(flag$fit[i,1])
    }
    qrcf.alpha <<- (C - E.L)/(sum(dt.sum$QRCF.95*dt.sum$Npolicies) - E.L)  # risk loading parameter 
    
    #-----------------------------
    # QRCF
    # dt.sum
    #-----------------------------
    dt.sum$QRCF <- dt.sum$Pure + qrcf.alpha*(dt.sum$QRCF.95 - dt.sum$Pure) # risk premium 
    dt.sum$loading.QRCF <- dt.sum$QRCF - dt.sum$Pure        # risk loading                  
    
    
    
    #-----------------------------
    # expectiel regression (EQR)
    # solve alpha
    #-----------------------------
    
    dt.sum$EQR.95 <- 0
    
    m3.e <- expectreg.ls((y) ~ x1 + x2 + x3, data = dt, expectiles = 0.95)
    flag <- predict(m3.e, newdata = dt.sum)
    dt.sum$EQR.95 <- (flag$fit)
    eqr.alpha <- (C - E.L)/(sum(dt.sum$EQR.95*dt.sum$Npolicies) - E.L) 
    
    
    
    #-----------------------------
    # EQR
    # dt.sum
    #-----------------------------
    dt.sum$EQR <- dt.sum$Pure + eqr.alpha*(dt.sum$EQR.95 - dt.sum$Pure) 
    dt.sum$loading.EQR <- dt.sum$EQR - dt.sum$Pure                       
    
    # #-----------------------------
    # # MSE
    # #-----------------------------
    
    mse.mat[k,] <- with(dt.sum, {
      c(sum(((QR - riskP))^2),
        sum(((QRCF - riskP))^2),
        sum(((QRII - riskP))^2),
        sum(((EQR - riskP))^2))/nrow(dt.sum)
    })

  }
  mean.mse <- apply(mse.mat, 2, mean)
  # mse for all models
  mse[j,] <- apply(mse.mat, 2, mean)
  # sample variance for all models
  svar.mse[j,] <- c(sum((mse.mat[,1] -  mean.mse[1])^2)/(Nsim - 1)/Nsim,
                    sum((mse.mat[,2] -  mean.mse[2])^2)/(Nsim - 1)/Nsim,
                    sum((mse.mat[,3] -  mean.mse[3])^2)/(Nsim - 1)/Nsim,
                    sum((mse.mat[,4] -  mean.mse[4])^2)/(Nsim - 1)/Nsim)

  
}

```

```{r message=FALSE, warning=FALSE}
load("D:/对外经济贸易大学 - 科研/0. Risk Loadings of Classification Ratemaking（in progress)/2021-final-code/mse_overall.RData")

row.names(mse) <- alpha.vector
row.names(svar.mse) <- alpha.vector
colnames(mse) <- c('QR', 'QRCF', "QRII" ,'EQR')
colnames(svar.mse) <- c('QR', 'QRCF', "QRII" ,'EQR')

kable(mse, digits = 2)
kable(svar.mse, digits = 2)

```

### Case: MSE and sample variance of the estimated risk premium for 8 tariff classes in the case of $\varphi=0.05,0.10,0.15$.

```{r eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(111)
Nsim <- 2000
alpha.vector <- c(0.05, 0.1, 0.15)
pars <- c(120, 1.65)
for(i in 1:8){
  assign(paste0("bias", i, ".mat"), matrix(0, nrow = Nsim, ncol = 4))
  assign(paste0("mse", i, ".mat"), matrix(0, nrow = Nsim, ncol = 4))
  assign(paste0("z", i, ".mat"), matrix(0, nrow = Nsim, ncol = 4))
  
  assign(paste0("bias", i, ".list"), list())
  assign(paste0("mse", i, ".list"), list())
  
  assign(paste0("bias", i), matrix(0, nrow = length(alpha.vector), ncol = 4))
  assign(paste0("mse", i), matrix(0, nrow = length(alpha.vector), ncol = 4))
  assign(paste0("var", i), matrix(0, nrow = length(alpha.vector), ncol = 4))
  
  
} 

for (j in 1:length(alpha.vector)){
  alpha <- alpha.vector[j]
for(k in 1:Nsim){
  nsample <- 5000
  x1sim <- rbinom(n = nsample, size = 1, prob = 0.6)
  x2sim <- rbinom(n = nsample, size = 1, prob = 0.8)
  x3sim <- rbinom(n = nsample, size = 1, prob = 0.5)
  beta <- c(4, 0.5, 0.5, 0.5)
  X <- model.matrix( ~ x1sim + x2sim + x3sim)
  mu <- as.vector(exp(X%*%beta))

  phi <- pars[1]
  p <- pars[2]
  # true value of C, Pure premium, and Risk prmeium
  C <- sum((1 + alpha)*mu) # risk loading parameter is 10% using expected value premium principle
  E.L <- sum(mu) # true pure premium
  riskP <- mu*(1 + alpha) # true risk premium for dt
  ysim <- 0
  for(i in 1:nsample){
    ysim[i] <- rtweedie(n = 1, mu = mu[i], phi = phi, power = p)
  }

  dt <- data.table(x1 = x1sim,
                   x2 = x2sim,
                   x3 = x3sim,
                   y = ysim,
                   clm = ifelse(ysim == 0, 0, 1))
  dt0 <- dt[y > 0]
  dt$count <- 1
  dt.sum     <- dt[, .( y = sum(y), Npolicies = sum(count)),
                   by = c('x1', 'x2', 'x3')
                   ]
  dt.sum <- dt.sum[order(x1, x2, x3)]

  m_clm     <- glm(clm ~ x1 + x2 + x3, family = binomial(link = "logit"), data = dt)
  X1        <- model.matrix( ~ x1 + x2 + x3, data = dt.sum)
  beta_pred <- coef(m_clm)
  eta_pred  <- X1%*%beta_pred
  pi.pred   <- 1 - (exp(eta_pred)/(1+exp(eta_pred)))
  dt.sum$pi.pred <- pi.pred
  dt.sum$mu <- exp(X1%*%beta)
  # true risk premium
  dt.sum$riskP <- (1 + alpha)*dt.sum$mu


  ## =========================================================================
  # Two-part GLMs: Logistic + gamma
  ## =========================================================================
  # 0-1 claim or not part
  m_clm     <- glm(clm ~ x1 + x2 + x3, family = binomial(link = "logit"), data = dt)
  X_pred    <- model.matrix( ~ x1 + x2 + x3, data = dt)
  beta_pred <- coef(m_clm)
  eta_pred  <- X_pred%*%beta_pred
  pi_pred   <- 1 - (exp(eta_pred)/(1+exp(eta_pred)))
  
  # claim > 0 claim amount part
  m.claim   <- glm(y ~ x1 + x2 + x3, family = Gamma(link='log'), data = dt0)
  X_pred    <- model.matrix( ~ x1 + x2 + x3, data = dt)
  beta_pred <- coef(m.claim)
  y_pred    <- exp(X_pred%*%beta_pred)
  
 
  
  #-----------------------------
  # dt.sum data set
  #-----------------------------
  X1        <- model.matrix( ~ x1 + x2 + x3, data = dt.sum)
  beta_pred <- coef(m_clm)
  eta_pred  <- X1%*%beta_pred
  pi.pred   <- 1 - (exp(eta_pred)/(1 + exp(eta_pred)))  # non-claim probability
  beta_pred <- coef(m.claim)
  mu        <- exp(X1%*%beta_pred)
  E.ga      <- (1 - pi.pred)*mu
 
  dt.sum$Pure    <- E.ga                     # pure

  
  ## ========================================================================
  # Two-part quantile regressions
  # QR & QRCF & & QRII ER
  ## ========================================================================
  
  theta <- 0.95
  dt.sum$theta_star <- (theta - dt.sum$pi.pred)/(1 - dt.sum$pi.pred)
  
  dt$QR.95 <- 0
  for(i in 1:nrow(dt.sum)){
    m.s     <- rq(log(y) ~ x1 + x2 + x3, data = dt0, tau = dt.sum$theta_star[i])  # QR model
    TraQuan <- exp(predict(m.s, newdata = dt.sum)) # prediction
    dt.sum$QR.95[i] <- TraQuan[i]
  }
  qr.alpha <<- (C - E.L)/(sum(dt.sum$QR.95*dt.sum$Npolicies) - E.L) 
  
  #-----------------------------
  # QR
  # Risk class prediction (dt.sum) 
  #-----------------------------
  dt.sum$QR <- dt.sum$Pure + qr.alpha*(dt.sum$QR.95 - dt.sum$Pure) 
  dt.sum$loading.QR <- dt.sum$QR - dt.sum$Pure                        
  
  
  #-----------------------------
  # QRII
  # Risk class prediction (dt.sum) 
  #-----------------------------
  theta_solve <- function(theta){
    m.s  <- rq(log(y) ~ x1 + x2 + x3, data = dt0, tau = theta) 
    flag <- exp(predict(m.s, newdata = dt.sum))*(1-dt.sum$pi.pred)
    bias <- C - sum(flag*dt.sum$Npolicies)
    return(bias)
  }
  upper_theta <- 0.99999
  lower_theta <- 0.00000001
  library(rootSolve)
  m_solve <- uniroot(f       = theta_solve,
                     lower   = lower_theta,
                     upper   = upper_theta,
                     maxiter = 50000,
                     tol     = .Machine$double.eps^0.525) 
  theta_Tra <- m_solve$root
  m.s  <- rq(log(y) ~ x1 + x2 + x3, data = dt0, tau = theta_Tra) 
  flag <- exp(predict(m.s, newdata = dt.sum))*(1-dt.sum$pi.pred)
  dt.sum$QRII <- flag
  
  #-----------------------------
  # QRCF
  # solve alpha
  #-----------------------------
  m3.s <- iqr(log(y) ~ x1 + x2 + x3,
              data      = dt0,
              formula.p = ~ slp(p,3))
  dt.sum$QRCF.95 <- 0
  for(i in 1:nrow(dt.sum)){
    flag <- predict(m3.s, type = "QF", p = dt.sum$theta_star[i], newdata = dt.sum)
    dt.sum$QRCF.95[i] <- exp(flag$fit[i,1])
  }
  qrcf.alpha <<- (C - E.L)/(sum(dt.sum$QRCF.95*dt.sum$Npolicies) - E.L) 
  
  #-----------------------------
  # QRCF
  # dt.sum
  #-----------------------------
  dt.sum$QRCF <- dt.sum$Pure + qrcf.alpha*(dt.sum$QRCF.95 - dt.sum$Pure) 
  dt.sum$loading.QRCF <- dt.sum$QRCF - dt.sum$Pure                        
  

  
  #-----------------------------
  # EQR
  # solve alpha
  #-----------------------------

  
  dt.sum$EQR.95 <- 0

  m3.e <- expectreg.ls((y) ~ x1 + x2 + x3, data = dt, expectiles = 0.95)
  flag <- predict(m3.e, newdata = dt.sum)
  dt.sum$EQR.95 <- (flag$fit)
  eqr.alpha <- (C - E.L)/(sum(dt.sum$EQR.95*dt.sum$Npolicies) - E.L) 
  
  
  
  #-----------------------------
  # EQR
  # dt.sum
  #-----------------------------
  dt.sum$EQR <- dt.sum$Pure + eqr.alpha*(dt.sum$EQR.95 - dt.sum$Pure)
  dt.sum$loading.EQR <- dt.sum$EQR - dt.sum$Pure
  
  # #-----------------------------
  # # MSE
  # #-----------------------------

  z0.mat <- cbind(dt.sum$QR, 
                 dt.sum$QRCF , 
                 dt.sum$QRII , 
                 dt.sum$EQR)
  
  mse0.mat <- cbind(dt.sum$QR - dt.sum$riskP, 
                    dt.sum$QRCF  - dt.sum$riskP, 
                    dt.sum$QRII  - dt.sum$riskP, 
                    dt.sum$EQR - dt.sum$riskP)^2
  
  bias0.mat <- cbind(dt.sum$QR - dt.sum$riskP, 
                     dt.sum$QRCF  - dt.sum$riskP, 
                     dt.sum$QRII  - dt.sum$riskP, 
                     dt.sum$EQR - dt.sum$riskP)
  
  z1.mat[k,] <- z0.mat[1,] # class 1
  z2.mat[k,] <- z0.mat[2,] # class 2
  z3.mat[k,] <- z0.mat[3,] # class 3
  z4.mat[k,] <- z0.mat[4,] # class 4
  z5.mat[k,] <- z0.mat[5,]
  z6.mat[k,] <- z0.mat[6,]
  z7.mat[k,] <- z0.mat[7,]
  z8.mat[k,] <- z0.mat[8,]
  
  
  
  bias1.mat[k,] <- bias0.mat[1,] # class 1
  bias2.mat[k,] <- bias0.mat[2,] # class 2
  bias3.mat[k,] <- bias0.mat[3,] # class 3
  bias4.mat[k,] <- bias0.mat[4,] # class 4
  bias5.mat[k,] <- bias0.mat[5,]
  bias6.mat[k,] <- bias0.mat[6,]
  bias7.mat[k,] <- bias0.mat[7,]
  bias8.mat[k,] <- bias0.mat[8,]
  
  
  mse1.mat[k,] <- mse0.mat[1,]
  mse2.mat[k,] <- mse0.mat[2,]
  mse3.mat[k,] <- mse0.mat[3,]
  mse4.mat[k,] <- mse0.mat[4,]
  mse5.mat[k,] <- mse0.mat[5,]
  mse6.mat[k,] <- mse0.mat[6,]
  mse7.mat[k,] <- mse0.mat[7,]
  mse8.mat[k,] <- mse0.mat[8,]
  
}
  
  mse1[j,] <- apply(mse1.mat, 2, mean)
  mse2[j,] <- apply(mse2.mat, 2, mean)
  mse3[j,] <- apply(mse3.mat, 2, mean)
  mse4[j,] <- apply(mse4.mat, 2, mean)
  mse5[j,] <- apply(mse5.mat, 2, mean)
  mse6[j,] <- apply(mse6.mat, 2, mean)
  mse7[j,] <- apply(mse7.mat, 2, mean)
  mse8[j,] <- apply(mse8.mat, 2, mean)
  
  
  bias1[j,] <- apply(bias1.mat, 2, mean)
  bias2[j,] <- apply(bias2.mat, 2, mean)
  bias3[j,] <- apply(bias3.mat, 2, mean)
  bias4[j,] <- apply(bias4.mat, 2, mean)
  bias5[j,] <- apply(bias5.mat, 2, mean)
  bias6[j,] <- apply(bias6.mat, 2, mean)
  bias7[j,] <- apply(bias7.mat, 2, mean)
  bias8[j,] <- apply(bias8.mat, 2, mean)
  
  var1[j,] <- apply(z1.mat, 2, sd)^2/Nsim
  var2[j,] <- apply(z2.mat, 2, mean)^2/Nsim
  var3[j,] <- apply(z3.mat, 2, mean)^2/Nsim
  var4[j,] <- apply(z4.mat, 2, mean)^2/Nsim
  var5[j,] <- apply(z5.mat, 2, mean)^2/Nsim
  var6[j,] <- apply(z6.mat, 2, mean)^2/Nsim
  var7[j,] <- apply(z7.mat, 2, mean)^2/Nsim
  var8[j,] <- apply(z8.mat, 2, mean)^2/Nsim
  
  
  mse1.list[[j]] <- mse1.mat
  mse2.list[[j]] <- mse2.mat
  mse3.list[[j]] <- mse3.mat
  mse4.list[[j]] <- mse4.mat
  mse5.list[[j]] <- mse5.mat
  mse6.list[[j]] <- mse6.mat
  mse7.list[[j]] <- mse7.mat
  mse8.list[[j]] <- mse8.mat
  
  bias1.list[[j]] <- bias1.mat
  bias2.list[[j]] <- bias2.mat
  bias3.list[[j]] <- bias3.mat
  bias4.list[[j]] <- bias4.mat
  bias5.list[[j]] <- bias5.mat
  bias6.list[[j]] <- bias6.mat
  bias7.list[[j]] <- bias7.mat
  bias8.list[[j]] <- bias8.mat
  

}

```

```{r message=FALSE, warning=FALSE}
load("D:/对外经济贸易大学 - 科研/0. Risk Loadings of Classification Ratemaking（in progress)/2021-final-code/mse_riskclass.RData")
mse.caseI <- rbind(mse1[1,], mse2[1,], mse3[1,], mse4[1,], mse5[1,], mse6[1,], mse7[1,], mse8[1,])
mse.caseII <- rbind(mse1[2,], mse2[2,], mse3[2,], mse4[2,], mse5[2,], mse6[2,], mse7[2,], mse8[2,])
mse.caseIII <- rbind(mse1[3,], mse2[3,], mse3[3,], mse4[3,], mse5[3,], mse6[3,], mse7[3,], mse8[3,])
colnames(mse.caseI) <- c('QR', 'QRCF', "QRII" ,'EQR')
colnames(mse.caseII) <- c('QR', 'QRCF', "QRII" ,'EQR')
colnames(mse.caseIII) <- c('QR', 'QRCF', "QRII" ,'EQR')
row.names(mse.caseI) <- riskclass
row.names(mse.caseII) <- riskclass
row.names(mse.caseIII) <- riskclass
mse.all <- rbind(mse.caseI, mse.caseII, mse.caseIII)
# mse
kable(mse.all, digits = 2)

```


## Section 5: Case study: Australian automobile insurance
### read data set from the local disk
```{r echo=TRUE, message=FALSE, warning=FALSE}
  dt            <- fread('C:/Users/Administrator/Desktop/expectile-regression-risk-loading/car.csv')
  dt$claimcst00 <- dt$claimcst0/dt$exposure
  dt$count   <- 1
  dt$veh_age <- factor(dt$veh_age, levels = c(2, 1, 3, 4))
  dt$agecat  <- factor(dt$agecat,  levels = c(5, 1, 2, 3, 4, 6))
  dt0        <- subset(dt, claimcst0 > 0)
  # data set for 24 risk classes
  dt.sum     <- dt[, .(Ncount    = sum(count), 
                       exposure  = sum(exposure), 
                       Npolicies = sum(count)),
                       by = c('veh_age', 'agecat')]
  
  # modelling claim probability
  m_clm     <- glm(clm ~ veh_age + agecat, family=binomial(link=logitexp(dt$exposure)), data=dt)
  X1        <- model.matrix( ~ veh_age + agecat, data=dt.sum)
  beta_pred <- coef(m_clm)
  eta_pred  <- X1%*%beta_pred
  pi.pred   <- 1 - (exp(eta_pred)/(1+exp(eta_pred))) 
  dt.sum$pi.pred <- pi.pred
  dt.sum    <- dt.sum[order(pi.pred)] # sort by the claim probability
  kable(dt.sum, digits = 3)
```

### total risk premium for the whole insurance portfolio

```{r message=FALSE, warning=FALSE}
C <- 22206147 # total risk premium that the insurer should charge
```


### Two-part GLMs: Logistic + gamma (EVPP + SDPP)
```{r echo=TRUE, message=FALSE, warning=FALSE}

 # 0-1 claim or not part
  m_clm     <- glm(clm ~ veh_age + agecat, family=binomial(link=logitexp(exposure=dt$exposure)), data=dt)
  X_pred    <- model.matrix( ~ veh_age + agecat, data = dt)
  beta_pred <- coef(m_clm)
  eta_pred  <- X_pred%*%beta_pred
  pi_pred   <- 1 - (exp(eta_pred)/(1+exp(eta_pred)))#*dt$exposure

  # claim > 0 claim amount part
  m.claim   <- glm(claimcst0 ~ veh_age + agecat, family = Gamma(link='log'), data = dt0)
  X_pred    <- model.matrix( ~ veh_age + agecat, data = dt)
  beta_pred <- coef(m.claim)
  y_pred    <- exp(X_pred%*%beta_pred)
 
  #--------------------------------------------------------------------------
  # solve the risk loading parameter in EVPP and SDPP: alpha.ga.E and alpha.ga.sd
  #--------------------------------------------------------------------------
  Dis_par <- 3.103186 # Dispersion parameter
  E.ga    <- (1 - pi_pred)*y_pred
  Var.ga  <- (1 - pi_pred)*y_pred^2*(pi_pred + Dis_par)
  sd.ga   <- sqrt(Var.ga)
  alpha.ga.E  <- C/sum(E.ga) - 1            # risk roading parameter in EVPP
  alpha.ga.sd <- (C - sum(E.ga))/sum(sd.ga) # risk roading parameter in SDPP
  c(alpha.ga.E*100, alpha.ga.sd*100)


  #----------------------------------------------------------
  # estimation of risk premium for 24 risk classes (dt.sum)
  #----------------------------------------------------------
  X1        <- model.matrix( ~ veh_age + agecat, data = dt.sum)
  beta_pred <- coef(m_clm)
  eta_pred  <- X1%*%beta_pred
  pi.pred   <- 1 - (exp(eta_pred)/(1 + exp(eta_pred)))
  
  beta_pred <- coef(m.claim)
  mu        <- exp(X1%*%beta_pred)
  E.ga      <- (1 - pi.pred)*mu
  var.ga    <- (1 - pi.pred)*mu^2*(pi.pred + Dis_par)
  sd.ga     <- sqrt(var.ga)

  dt.sum$Pure    <- E.ga                     # pure premium
  dt.sum$SDPP    <- E.ga + alpha.ga.sd*sd.ga # risk premium in EVPP
  dt.sum$EVPP    <- E.ga + alpha.ga.E*E.ga   # risk premium in SDPP

  dt.sum$loading.E  <- dt.sum$EVPP - dt.sum$Pure  # risk loading in EVPP
  dt.sum$loading.sd <- dt.sum$SDPP - dt.sum$Pure  # risk loading in EVPP

 
```


### QRII

```{r message=FALSE, warning=FALSE}
  theta_Tra <- 0.7908
  m.QRII  <- rq(log(claimcst0) ~ veh_age + agecat, data = dt0, tau = theta_Tra) 
  dt.sum$QRII <- exp(predict(m.QRII, newdata = dt.sum))*(1-dt.sum$pi.pred)
```

### QR
```{r message=FALSE, warning=FALSE}
 # solve the risk loading parameter
  theta <- 0.95  # quantile level for aggregate claim amount
  dt.sum$theta_star <- (theta - dt.sum$pi.pred)/(1 - dt.sum$pi.pred) # quantile level for non-zero aggregate claim amount
  E.L <- sum(dt.sum$Pure*dt.sum$Npolicies) # total pure premium
  dt.sum$QR.95 <- rep(NA,24)
  for(i in 1:24){
    m.s     <- rq(log(claimcst0) ~ veh_age + agecat, data = dt0, tau = dt.sum$theta_star[i])  # QR model
    TraQuan <- exp(predict(m.s, newdata = dt.sum))
    dt.sum$QR.95[i] <- TraQuan[i]
  }
  qr.alpha <- (C - E.L)/(sum(dt.sum$QR.95*dt.sum$Npolicies) - E.L) # risk loading parameter
  qr.alpha

  # Risk class prediction (dt.sum) 
  dt.sum$QR <- dt.sum$Pure + qr.alpha*(dt.sum$QR.95 - dt.sum$Pure) 
  dt.sum$loading.QR <- dt.sum$QR - dt.sum$Pure                     
```


### PQR
```{r message=FALSE, warning=FALSE}
 # solve the risk loading parameter in QPP
  m3.s <- iqr(log(claimcst0) ~ veh_age + agecat,
                data      = dt0,
                formula.p = ~ slp(p,3))
    
  dt.sum$QRCF.95 <- rep(NA,24)
  for(i in 1:24){
    flag <- predict(m3.s, type = "QF", p = dt.sum$theta_star[i], newdata = dt.sum)
    dt.sum$QRCF.95[i] <- exp(flag$fit[i,1])
  }
  qrcf.alpha <- (C - E.L)/(sum(dt.sum$QRCF.95*dt.sum$Npolicies) - E.L) 
  qrcf.alpha # the risk loading parameter
  

  # Risk class prediction (dt.sum) 
  dt.sum$PQR <- dt.sum$Pure + qrcf.alpha*(dt.sum$QRCF.95 - dt.sum$Pure) # prediction in PQR for 24 tariff classes
  dt.sum$loading.PQR <- dt.sum$PQR - dt.sum$Pure   

```



### ER
```{r message=FALSE, warning=FALSE}
  # solve the risk loading parameter
  library(expectreg) # expectreg.ls
  library(dummies) # generate the dummies
  ohe_feats <- names(dt)[sapply(dt, is.factor)]
  df_all <- dt
  df_all_sum <- dt.sum
  for (f in ohe_feats){
    df_all <- dummy.data.frame(df_all, names = f, sep = "_")
    df_all_sum <- dummy.data.frame(df_all_sum, names = f, sep = "_")
  }

  dt.sum$EQR.95 <- rep(NA,24)
  m3.e <- expectreg.ls((claimcst0) ~ agecat_1  + agecat_2 + agecat_3 + agecat_4 + agecat_6
                       + veh_age_1 + veh_age_3 + veh_age_4, data = df_all, 
                       expectiles = 0.95,
                       ci = T)
  flag <- predict(m3.e, newdata = df_all_sum)
  dt.sum$EQR.95 <- (flag$fit)
  eqr.alpha <- (C - E.L)/(sum(dt.sum$EQR.95*dt.sum$Npolicies) - E.L) 
  eqr.alpha # the risk loading parameter in EPP
  
  
  # Risk class prediction (dt.sum) 
  dt.sum$EQR  <-  dt.sum$Pure + eqr.alpha*(dt.sum$EQR.95 - dt.sum$Pure) # prediction in EQR for individual polices
  dt.sum$loading.EQR  <-  dt.sum$EQR - dt.sum$Pure                         # risk loading
 
  
```


### Risk premium comparsion

```{r message=FALSE, warning=FALSE}

dt.out <- dt.sum[,c('veh_age','agecat',"pi.pred",
           'Pure', 'EVPP', 'SDPP',
           'QR','QRII','PQR','EQR')]
kable(dt.out, digits = 2)
```


